# Assignments and Grading
This section provides general details on the different types of assignments for this course. It also contains policies for submitting work, receiving feedback, and late work.

## Assignments

Your grade for this course will consist of a number of different assignments on which points may be earned. Each category of assignment is described below.

### Attendance and Participation

```{block, type = "rmdtip"}
Attendance and participation are worth **10%** of your final grade
```

As discussed above, both attendance and participation are important aspects of this class. The class participation grade will be based on (a) attendance, (b) level of engagement during class, and (c) class "entry" and "exit tickets".

Each of these elements is assigned a point value and assessed using a scale that awards full, partial, or no credit. Not attending class or completing an "entry" or "exit" ticket will result in no credit being earned for that element on a given day. Disengagement during class may result in partial or no credit being earned. Late arrivals will result in only partial credit earned for that element on a given day.

Your participation grade will be split, with 25 points (5% of your final grade) for the first half of the semester (through Week 8) and another 25 points (5%) for the second half (Weeks 9 to 17). Since the number of points awarded for participation are variable, the total number of points earned for each half will be **weighted** so that it is converted to a 0 to 25 scale. I provide the final number of points earned for each half of the course. If you would like a more detailed breakdown of your participation grade and/or attendance record, please reach out and I will happily provide one.

"Entry" and "exit" tickets will be collected via **[Google Classroom](https://classroom.google.com)**. These will only be graded for students who present in class on the day that they were collected. Students without access to a smartphone or laptop should submit their tickets as soon as possible after class on the days the tickets are collected. Beginning and end of the semester activities, like the 'Student Information Sheet' and the 'Speaking Up In Class Survey', are counted as "entry" tickets.

### Sociological Experiences

```{block, type = "rmdtip"}
Sociological experiences are worth **10%** of your final grade
```

Students will be required to complete two sociological experiences and write a short response paper summarizing your own experience. Additional details and a grading rubric are available on **[Google Classroom](https://classroom.google.com)** under the 'Classwork' tab. "The Bus" will be due on **Tuesday, October 1^st^** and "The Suitcase" will be due on **Thursday, November 7^th^**. Each reflection paper is worth 5% of your final grade.

### QHQ Papers

```{block, type = "rmdtip"}
QHQ Papers are worth **20%** of your final grade
```

Each student will write a QHQ reflection paper on three chapters (one chapter per discussion period) of *Mama Might Be Better Off Dead* (Abraham 1993). These reflection papers will integrate previous lecture material and readings to understand the cycle of events described in the book. Additional details and a grading rubric are available on **[Google Classroom](https://classroom.google.com)** under the 'Classwork' tab. QHQ Paper 1 will be due on **Thursday, October 10^th^**, QHQ Paper 2 will be due on **Thursday, November 14^th^**, and QHQ Paper 3 will be due on **Tuesday, December 3^rd^**. QHQ Paper 1 is ungraded. If it is not turned in or not taking seriously, however, a deduction of 3% will be applied to your final grade. QHQ Papers 2 and 3 each count for 10% of your final grade.

### Exams

```{block, type = "rmdtip"}
Exams are worth **60%** of your final grade
```

Three non-cumulative multiple choice exams will be given throughout the semester. Each exam will cover the breadth of the material in the course, including readings, lectures, and videos. Exam 1 will be given on **Tuesday, September 24^th^**, Exam 2 will be given on **Thursday, October 31^st^**, and Exam 3 will be given during our class's schedule final exam period on **Tuesday, December 17^th^**. Please note that Exam 3 will be held at a slightly different time (from 8am to 9:50am, though its format will be the same as the priort exams and most students should not need the full time period). Each exam is worth 20% of your final grade.

## Submission and Late Work

### Google Classroom Submissions

All assignments must be submitted via **[Google Classroom](https://classroom.google.com)** *as a Google Doc file* unless otherwise noted in the assignment instructions. **[Google Classroom](https://classroom.google.com)** will have submission portals for each assignment in the `Coursework` tab. Create your file in Google Docs and then use the submission portal to submit the file. Do not upload a `.pdf`, `.docx`, `.doc`, or other file format - you must submit a **Google Doc file**. Once submitted, you will not be able to edit the file again until it is returned with feedback and a grade. Feedback will be returned to students via comments embedded in each Google Doc.

The Google Doc submission policy is in place because it facilitates clear, easy grading that can be turned around to you quickly. Submitting assignments in ways that deviate from this policy will result in a late grade (see below) being applied in the first instance and a zero grade for each subsequent instance. If you have questions about how to use Google Docs or Google Classroom, or believe there has been an issue with your submission, please reach out to me **before** the submission deadline.

### Late Work

Once the due date has passed, any assignments shared will be treated as late. Be advised that Google time-stamps submissions, so that even being a few seconds over the due date and time will result in your assignment being marked late. Like arriving late to class, this happens automatically, so please let me know as soon as possible **before** class if you have a concern about a potentially late submission. 

Assignments shared within 24-hours of the due date will have 15% deducted from the grade. I will deduct 15% per day for the next two 24-hour periods that assignments are late; after 72-hours, I will not accept late work. If you cannot submit work on time because of a personal illness, a family issue, jury duty, an athletic match, or a religious observance, you must contact me beforehand to discuss alternate submission of work. Internet or computer issues are not grounds for missed deadlines. I may ask for more information, such as a note from a physician, a travel letter from Athletics, or other documentation for absences. 

### Missed Exams

If you cannot attend an exam due to a personal illness, a family issue, jury duty, an athletic match, or a religious observance, you must contact me **beforehand** to discuss alternate exam scheduling. I may ask for more information, such as a note from a physician, a travel letter from Athletics, or other documentation for absences. Unless there is an extreme situation, such as emergency hospitalization, I do not allow students to make up exams if I have not been notified prior to the original exam date.

Since the final exam schedule is not yet available, please do not book travel home at the end of the semester until you know the date of the third exam - I cannot accommodate students who request an alternative exam date due to travel conflicts.

## Extra Credit

From time to time I may offer extra credit to be applied to your final grade. I will only offer extra credit if it is open to the entire class (typically for something like attending a lecture or event on-campus). If I offer extra credit, I will generally require you to submit a short written summary of the activity within a week of the event to obtain the credit. Papers should be submitted via **[Google Classroom](https://classroom.google.com)**. When offered, extra credit opportunities cannot be made-up or substituted if you are unable to attend the event.

## Grading

I use a point system for calculating grades. The following table gives the weighting and final point totals for all assignments for this course:

```{r, echo=FALSE}
points <- data.frame(
  Assignment = c("Participation", "Sociological Experiences", "QHQs", "Exams"),
  Points = c("25 pts", "25 pts", "50 pts", "100 pts"),
  Quantity = c("x2", "x2", "x2", "x3"),
  Total = c("50 pts", "50 pts", "100 pts", "300 pts"),
  Percent = c("10%", "10%", "20%", "60%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  points, booktabs = TRUE,
  caption = "SOC 1120 Points Breakdown"
)
```

All feedback will include grades that represent number of points earned. If you want to know your percentage on a particular assignment, divide the number of points earned by the number of points possible and then multiply it by 100.

Some of the provided rubrics on **[Google Classroom](https://classroom.google.com)** result in final points for assignments that include decimals. In the event of non-standard decimals (those other than .25, .5, or .75), I will round your grade up to the next standard decimal value (e.g. .25, .5, or .75).

### Conflicting or Incorrect Grades

Assignment grades will generally be given both as a comment in the Google Doc itself and on Google Classroom. If you notice a discrepancy between the grade you received in the feedback and what appears on Google Classroom, please let me know as soon as possible. I will default to taking the higher of the two grades as the official grade.

Since exams and scantrons are handed back in class, I will only consider possible scantron scoring errors that I am made aware of at the end of class on the day that exams are returned. Please make sure to discuss any concerns you have about your scantron with me that day. As with other assignments, if there is a discrepancy between the grade noted on your exam and what is entered on Google Classroom, I will default to taking the higher of the two grades as the official grade.

### Final Grades

Final grades will be calculated by taking the sum of all points earned and dividing it by the total number of points possible (500). This will be multiplied by 100 and then converted to a letter grade using the
following table:

```{r, echo=FALSE}
grades1 <- data.frame(
  GPA = c("4.0", "3.7", "3.3", "3.0", "2.7"),
  Letter = c("A", "A-", "B+", "B", "B-"),
  Percent = c("93.0% - 100%", "90.0% - 92.9%", "87.0% - 89.9%", "83.0% - 86.9%", "80.0% - 82.9%"),
  stringsAsFactors = FALSE
)

grades2 <- data.frame(
  GPA = c("2.3", "2.0", "1.7", "1.0", "0.0"),
  Letter = c("C+", "C", "C-", "D", "F"),
  Percent = c("77.0% - 79.9%", "73.0% - 76.9%", "70.0% - 72.9%", "63.0% - 69.9%", "< 63.0%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  list(
    grades1,
    grades2
  ),
  caption = "Course Grading Scale", booktabs = TRUE
)
```

### Revisions and Incompletes

No chances will be given for revisions of poor grades. Incomplete grades will be given upon request only if you have a "C" average and have completed at least two-thirds of the possible points (330 points). You should note that incomplete grades must be rectified by the specified deadline or they convert to an "F".
