# (PART) Reading List {-}

# Course Schedule

The following is a high-level schedule that details the general topic covered by each module. Modules are collections of two or more lectures and class discussions under the broad headings provided below.

```{r, echo=FALSE}
schedule <- dplyr::tibble(
  Part = c("**1**", "1", "1", "**2**", "2", "2", "2", "**3**", "3", "3", "3", "**4**", "4"),
  Module = c("", "1", "2", "", "3", "4", "5", "", "6", "7", "8", "", "9"),
  `Planned Start Date` = c("", 
                           "August 18^th^", 
                           "September 1^st^",
                           "",
                           "September 15^th^",
                           "September 22^nd^",
                           "October 6^th^",
                           "",
                           "October 13^th^",
                           "November 3^rd^",
                           "November 10^th^",
                           "",
                           "November 17^th^"),
  Title = c("**Thinking Like Sociologists**",
            "Engaging the Social World",
            "Structuring the Social World",
            "**The Building Blocks of Society**",
            "Culture",
            "Socioeconomic Status",
            "Gender and Sexuality",
            "**The Broken Heart of America**",
            "Race and Racism",
            "Intersectionality",
            "Urban Sociology",
            "**Course Conclusion**",
            "Course Conclusion")
)

knitr::kable(
  schedule, booktabs = TRUE,
  caption = "SOC 1120 Course Overview"
)
```

### Assignment Due Dates

All assignments are due by the beginning of class unless otherwise noted, and all times are in Central time.

```{r, echo=FALSE}
schedule <- dplyr::tibble(
  Date = c("**August**",
           "Thursday, August 20^th^",
           "Sunday, August 30^th^",
           "**September**",
           "Tuesday, September 1^st^",
           "Thursday, September 10^th^",
           "Monday, September 14^th^",
           "Sunday, September 20^th^",
           "Tuesday, September 22^nd^",
           "Tuesday, September 29^th^",
           "**October**",
           "Thursday, October 1^st^",
           "Monday, October 12^th^",
           "Thursday, October 29^th^",
           "**November**",
           "Sunday, November 1^st^",
           "Tuesday, November 3^rd^",
           "Tuesday, November 3^rd^",
           "Thursday, November 12^th^",
           "Tuesday, November 17^th^",
           "Sunday, November 22^nd^",
           "Monday, November 23^rd^",
           "Tuesday, November 24^th^",
           "Monday, November 30^th^"
           ),
  Time = c("", "", "5pm", "", "", "", "", "5pm", "", "", "", "", "", "", "", "5pm", "", "", "", "", "5pm", "", "", ""),
  Assignment = c("",
                 "Student Information Sheet", 
                 "Theory Isn't Dead Post 1", 
                 "",
                 "Theory Isn't Dead Follow-up 1", 
                 "Sociological Experience 1",
                 "Quiz 1",
                 "Theory Isn't Dead Post 2", 
                 "Theory Isn't Dead Follow-up 2", 
                 "Sociological Experience 2",
                 "",
                 "QHQ Paper 1",
                 "Quiz 2",
                 "Sociological Experience 3",
                 "",
                 "Theory Isn't Dead Post 3", 
                 "Theory Isn't Dead Follow-up 3", 
                 "QHQ Paper 2",
                 "Sociological Experience 4",
                 "QHQ Paper 3",
                 "Theory Isn't Dead Post 4", 
                 "Quiz 3",
                 "Theory Isn't Dead Follow-up 4",
                 "Final Project")
)

knitr::kable(
  schedule, booktabs = TRUE,
  caption = "SOC 1120 Assignment Timeline"
)
```

### Scheduling Notes

The course schedule may change as it depends on the progress of the class and the [challenges we are confronted by this semester](covid-19.html). The web version of this document will be updated to reflect any alterations, but the `.pdf` version will remain unaltered.
